A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-22 paper/paper.tex
Spacing
Presolve

The use of bitset encodings for graph algorithms to exploit hardware parallelism dates back to at
least Ullmann's algorithm \cite{Ullmann:1976}, and remains an active area of research
\cite{SanSegundo:2007,Ullmann:2011}. We use bitsets here: our graphs are stored as arrays of bit
vectors, our domains are bit vectors, the neighbourhood intersection in \cref{algorithm:assign} is a
bitwise-and operation, the unions in \cref{algorithm:search} and \cref{algorithm:cad} are bitwise-or
operations, and the cardinality check in \cref{algorithm:cad} is a population count (this is a
single instruction in modern CPUs).  In addition to the SIMD-like parallelism from bitset encodings,
we observed two opportunities for multi-core thread parallelism in the algorithm:

@@

Although overall ours is the single best solver, VF2 is stronger on trivial instances. This is not
surprising: we must spend time constructing supplemental graphs. Thus it may be worth using VF2 as a
presolver, if short runtimes for trivial instances is desirable---this may be the case in graph
database systems where many trivial queries must be run \cite{Giugno:2013} (although these systems
could cache the supplemental graphs for targets). These results also suggest potential scope for
algorithm portfolios, or instance-specific configuration: for example, we could omit or use
different supplemental graphs in some cases.

>>>>

The use of bitset encodings for graph algorithms to exploit hardware parallelism dates back to at
least Ullmann's algorithm \cite{Ullmann:1976}, and remains an active area of research
\cite{SanSegundo:2007,Ullmann:2011}. We use bitsets here: our graphs are stored as arrays of bit
vectors, our domains are bit vectors, the neighbourhood intersection in \cref{algorithm:assign} is a
bitwise-and operation, the unions in \cref{algorithm:search} and \cref{algorithm:cad} are bitwise-or
operations, and the cardinality check in \cref{algorithm:cad} is a population count (this is a
single instruction in modern CPUs).

In addition to the SIMD-like parallelism from bitset encodings, we observed two opportunities for
multi-core thread parallelism in the algorithm:

@@

Although overall ours is the single best solver, VF2 is stronger on trivial instances. This is not
surprising: we must spend time constructing supplemental graphs. Thus it may be worth using either
VF2 or our own algorithm without supplemental graphs as a presolver, if short runtimes for trivial
instances is desirable---this may be the case in graph database systems where many trivial queries
must be run \cite{Giugno:2013} (although these systems could cache the supplemental graphs for
targets). These results also suggest potential scope for algorithm portfolios, or instance-specific
configuration: for example, we could omit or use different supplemental graphs in some cases.
